---
title: "A DFT study to development a SiO2 mesoporous surface model"
author: "Ciellie Jansen van Vuuren"
date: "12/6/2017"
output: html_document
bibliography: library.bib
csl: oxford-university-press-scimed-numeric.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction

Grubbs catalysts for alkene metathesis have a vast range of advantages, but the fact that these catalysts are homogeneous makes extraction of the catalyst from the post-reaction mixtures very difficult. Because of cost implications, the re-use of the catalyst became very important [1].[@RN33]

A heterogeneous catalyst can be a solution to the above-mentioned issue. In general, the activity and selectivity of heterogeneous catalysts are lower than homogeneous catalysts, but the advantage of separation, recovery and recycling outweigh these shortcomings.

According to literature mesoporous support materials, are ideal heterogeneous support materials [2,3]. In this study, we decided to focus on the SBA-15 and MCM-41 mesoporous support material.

The first step in modelling a SBA-15 or MCM-41 mesoporous surface is to create an amorphous SiO2 bulk using an alpha-quartz (space group 180). The 3X3X3 supercell was submitted to dynamics studies using Materials Studio's CASTEP module and VASP 5.3 [4,5]. This was done and I will discuss the procedure that I followed to accomplish this.

To do surface calculations it became very difficult, using the amorphous SiO2 bulk. We decide to use a crystalline 3X3X3 SiO2 bulk, using VASP 5.3. An Ab Initio Molecular Dynamics study will be done on all surfaces using VASP 5.3. A comparison between the amorphous and crystalline surfaces will be discussed

#Experimental work 2017

###1. Amorphous SiO~2~ Bulk
###2. K-point energy convergence
###3. Determine surface energies
   + This tutorials show the basic principals for calculating surface characteristics [@surf1] [@surf2]

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
